method

### 2022-06-07 06_Paper/ER-ED/method.Rmd
Update method.Rmd
under analyis plan: changed "active viewing" to "active viewing - negative" in H4a to make it consistent to the other Hypotheses

*Effects of emotion regulation on arousal, facial EMG and effort.* <br> 
To investigate the effects of the three ER strategies on subjective arousal (H2a), another rmANOVA  with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for subjective arousal ratings will be conducted.
To examine the effects of the three ER strategies on physiological responding (H3a and H3b), another rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for EMG *corrugator* and *levator* activity will be conducted.
To examine the effect of ER strategies on subjective effort (H4a), a rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective effort ratings will be conducted.

>>>>

*Effects of emotion regulation on arousal, facial EMG and effort.* <br> 
To investigate the effects of the three ER strategies on subjective arousal (H2a), another rmANOVA  with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for subjective arousal ratings will be conducted.
To examine the effects of the three ER strategies on physiological responding (H3a and H3b), another rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for EMG *corrugator* and *levator* activity will be conducted.
To examine the effect of ER strategies on subjective effort (H4a), a rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for subjective effort ratings will be conducted.
